### 2016-12-20 bundle.tex
Moved preamble

\subsection{The model}
% TODO http://tex.stackexchange.com/a/155317/5966 ?
\begin{figure}
\centering
\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
\input{pic/resonator_bundle.tex}
\end{tikzpicture}
\caption{Квантовый граф $\Gamma$, состоящий из полубесконечных ребер $\Omega_L, \Omega_R$ и рассеивателя $\Omega$, представляющего из себя $W$ идентичных ребер длины 1. В вершинах $V_a$, $V_b$ находятся $\delta$-образные потенциальные ямы глубины $a$ и $b$ соответственно.}\label{fig:res_bundle}
\end{figure}

@@

In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$. Таким образом, поведение интеграла зависит только от поведения множителя:

>>>>

\subsection{The model}
% TODO http://tex.stackexchange.com/a/155317/5966 ?
\begin{figure}
\centering
\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
\input{pic/resonator_bundle.tex}
\end{tikzpicture}
\caption{Quantum graph $\Gamma$, consisting of semi infinite edges  $\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
\label{fig:res_bundle}
\end{figure}

@@

In our case $x_0 = \frac{V}{4}$, $a = \frac{1}{2 V}(V^2 - 1)$, $b = Z$, and we can see that the integral is bounded by a constant independent of $R$ and $C$. Hence, the behaviour of the integral only dependends on the behaviour of the multiplier:
